--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---


```{r setup, include=FALSE, dev="CairoPNG"}
# the setup chunk MUST be at the very first code chunk of the .Rmd document in order to execute on the HPC because the cluster doesn't have certain graphical libraries installed
knitr::opts_chunk$set(
  echo = FALSE,
  error = TRUE,
  dev="CairoPNG"
)
options(bitmapType='cairo')
```

```{r htmlTemp3, echo=FALSE, eval=TRUE}
# https://stackoverflow.com/a/45501553
codejs <- readr::read_lines("js/codefolding.js")
collapsejs <- readr::read_lines("js/collapse.js")
transitionjs <- readr::read_lines("js/transition.js")

htmlhead <- 
  paste('
<script>',
paste(transitionjs, collapse = "\n"),
'</script>
<script>',
paste(collapsejs, collapse = "\n"),
'</script>
<script>',
paste(codejs, collapse = "\n"),
'</script>
<style type="text/css">
.code-folding-btn { margin-bottom: 4px; }
.row { display: flex; }
.collapse { display: none; }
.in { display:block }
</style>
<script>
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>
', sep = "\n")

readr::write_lines(htmlhead, path = "header.html")
```

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


This is an R code chunk:
```{r echo=TRUE}
a <- 10
b <- 5
a + b
```

